Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-13 treestats_paper.tex
fixed last paragraph about time

% visualization and time decomposition adding a new dimension
\krt{this para needs to go, right, now that the related results are offloaded
into a new tex file? Perhaps say that we can do this sort of thing?}
Genomic data are naturally distributed along two axes: along the genome, and across geography.
The tree sequence extends this to a third axis: time.
A great many methods in population genetics aim to describe aspects of history,
and accurate (or at least unbiased) tree sequence inference
may shift the focus of these problems from inference to descriptive analysis.
In this paper, we have made an exploratory foray in this direction,
by describing the time of origin of the ``admixture'' signal of nonzero $f_4$
between several subsets of the 1000 Genomes dataset,
in several inferred tree sequences.
It is not yet clear whether these time profiles tell us more about history
or about biases of the inference methods,
but either result would be useful.

>>>>

% visualization and time decomposition adding a new dimension
Genomic data are naturally distributed along two axes: along the genome, and across geography.
The tree sequence extends this to a third axis: time.
A great many methods in population genetics aim to describe aspects of history,
and accurate (or at least unbiased) tree sequence inference
may shift the focus of these problems from inference to descriptive analysis.
The methods we develop here distribute the contribution to various statistics across each tree,
and so could also be used to summarise contributions to various statistics across \emph{time}.
This could provide, for instance, the time distribution of mutations or branches
contributing positively or negatively to $f_4$ statistics of introgression,
which could help historical interpretations of these signals.
This additional summarization mode, however, is postponed for future work.
